### 2022-03-08 paper/output/document/thesis_4_applications.tex
ugh

%
\begin{isabellebody}%
\setisabellecontext{thesis{\isacharunderscore}{\isadigit{4}}{\isacharunderscore}applications}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsection{Applications \label{applications}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
In this chapter, I demonstrate that my system can produce correct judgements on challenging moral 
dilemmas that naive ethical reasoning cannot satisfactorily handle. My system can reproduce complex
ethical judgements because it is faithful to philosophical literature.
These dilemmas serve as examples of how my system could be used
in practice and demonstrate my system's ability to formalize longer, more complicted ethical arguments
than those presented in Chapter \ref{details}. 
Many of the tests in Section \ref{testing} perform metaethical reasoning, which analyzes properties
of morality itself and involves questions about the nature of ethical truth. In this chapter, I perform
``applied ethical reasoning," which is the use of ethics to resolve dilemmas and make judgements about 
what an agent should or should not do. This is the kind of reasoning necessary for an AI agent using my system to
navigate the real world.

@@

In this chapter, I attempt to tackle this challenge by
endowing my system with this kind of common sense in the specific case of lying. In order for my 
system to perform applied ethical reasoning, it will need common sense facts and definitions, like
those I present in this chapter. My system contributes the ability to reason
using the Formula of Universal Law, but this reasoning must be applied to objects that are defined
using common sense. In this chapter, I describe such common sense for the specific example
of lying.

>>>>

%
\begin{isabellebody}%
\setisabellecontext{thesis{\isacharunderscore}{\isadigit{4}}{\isacharunderscore}applications}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsection{Applications \label{applications}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
In this chapter, I demonstrate that my system can produce correct judgements for challenging moral 
dilemmas that naive ethical reasoning cannot satisfactorily handle. Because my system is faithful to
philosophical literature, it can reproduce complex ethical judgements presented by philosophers as 
solutions to controversial open questions in ethics.
These dilemmas serve as examples of how my system could be used
in practice and demonstrate my system's ability to formalize longer, more complicted ethical arguments
than those presented in Chapter \ref{details}.

Many of the tests in Section \ref{testing} perform metaethical reasoning, which analyzes properties
of morality itself and involves questions about the nature of ethical truth. In this chapter, I perform
``applied ethical reasoning,'' which is the use of ethics to resolve dilemmas and make judgements about 
what an agent should or should not do. This is the kind of reasoning necessary for an AI agent using my system to
navigate the real world.

@@

In this chapter, I tackle this challenge by
endowing my system with this kind of common sense in the specific case of lying. My system needs common 
sense facts and definitions because, while it has the ability to reason
using the Formula of Universal Law, this reasoning must be applied to objects that are defined
using common sense.
